Filamentary transport in high-power H-mode conditions and in no/small-ELM regimes to predict heat and particle loads on PFCs for future devices

### 2018-05-23 Meetings/23.05.2018.mst1tfm/mst1tfm_topic21_vianello.tex
Update to TeX file for MST1 meeting 23.05

\usepackage[style=nature,citestyle=authoryear-comp,defernumbers=true,maxnames=2,firstinits=true,
uniquename=init,backend=bibtex8,arxiv=abs,mcite]{biblatex}
\bibliography{../biblio}
\renewcommand*{\bibfont}{\footnotesize}
\renewcommand*{\citesetup}{\footnotesize}
\usepackage[export]{adjustbox}
\makeatother
\mode<presentation>
\makeatletter
% add a macro that saves its argument
\newcommand{\footlineextra}[1]{\gdef\insertfootlineextra{#1}}
\newbox\footlineextrabox
% for reducing font on a single slide
\newcommand\Fontvi{\fontsize{8}{7.2}\selectfont}
\title{Filamentary transport in high-power H-mode conditions and in no/small-ELM regimes to predict heat and particle loads on PFCs for future devices}
\date{23 May 2018}
\author[N.Vianello]{presented by N. Vianello on behalf of  MST1-Topic 21
  scientific team}
\begin{document}
\tikzstyle{every picture}+=[remember picture]
\maketitle
\begin{frame}{Scientific team}
  \centering{
  Volker Naulin, Matteo Agostini, Diogo Aguiam, Scott Allan, Matthias Bernert, Daniel Carralero Ortiz, 
Stefan Costea, Istvan Cziegler, Hugo De Oliveira, Joaquin Galdon-Quiroga, Gustavo Grenfell, Antti Hakola, 
Codrina Ionita-Schrittwieser, Heinz Isliker, Alexander Karpushov,
Jernej Kovacic, Benoît Labit, Bruce Lipschultz, 
Roberto Maurizio, Ken McClements, Fulvio Militello, Jeppe Miki Busk Olsen, Jens Juul Rasmussen, Timo Ravensbergen, Bernd Sebastian Schneider, Roman Schrittwieser, Jakub Seidl, Monica Spolaore, Christian Theiler, Cedric Kar-Wai Tsui, Kevin Verhaegh, Jose Vicente, 
Nickolas Walkden, Zhang Wei, Elisabeth Wolfrum, W. Vijvers}
\end{frame}

\begin{frame}{Background}
  \only<1>{
\begin{itemize}
\item Role of turbulence transport in the SOL saturation is a well
  know
  feature \parencite{LaBombard:2001ks,Rudakov:2005ic,Garcia:2007hh,Carralero:2014gs}. \textcolor{red}{Increasing
  density, even without reaching detachment SOL profile tend to flatten}
\end{itemize}}
% \only<2-3>{
%   \begin{columns}
%     \begin{column}{0.5\textwidth}
%       \begin{itemize}
%       \item Present understanding suggests that a transition of filament
%         propagation regime is dominated by effective
%         collisionality $\Lambda$ \parencite{Myra:2006p2754}
%         \begin{equation*}
%           \Lambda = \frac{L_{\parallel}/c_s}{1/\nu_{ei}}\frac{\Omega_i}{\Omega_e}
%         \end{equation*}
%         \item<3> \textcolor{red}{At constant blob size, increasing
%             collisionality provide a change in the filaments velocity
%             scaling properties}
%       \end{itemize}
%     \end{column}
%     \begin{column}{0.5\textwidth}
% %      \includegraphics<2>[width=\textwidth]{../pdfbox/Presentation/FigMyra}
%         \begin{tikzonimage}[width=\textwidth]{../generalFigures/FigMyra}
%           \only<3>{
%             \draw [->, ultra thick, red] (0.7,0.3) -- (0.7,0.6);}
%         \end{tikzonimage}
%     \end{column}
%   \end{columns}
% }
\only<2-4>{
  \begin{columns}
    \begin{column}{0.5\textwidth}
      \begin{itemize}
      \item AUG and JET (HT) \parencite{Carralero:2015gu} suggest that $\Lambda_{div}=\frac{L_{\parallel}/c_s}{1/\nu_{ei}}\frac{\Omega_i}{\Omega_e}$ dominates this
        process and a transition from
        \textcolor{ta3chameleon}{sheath-limited}
        \onslide<3-4>{to \textcolor{blue}{inertial regime}} 
        \item<4> \textcolor{red}{Tested by changing n$_e$
            and $T_e$ through fueling/seeding/heating}
      \end{itemize}
    \end{column}
    \begin{column}{0.5\textwidth}
      \begin{tikzonimage}[width=\textwidth]{../generalFigures/KoMFig2.png}
        \only<2-4>{
          \draw [thick, ta3chameleon, thick] (0.45,0.25) ellipse (0.23 and 0.1);
      }
        \only<3-4>{
          \draw [thick, blue, thick, rotate=-4] (0.8,0.55) ellipse (0.1 and 0.33);
      }
        \only<4>{
          \draw [thick, red, thick, dashed] (0.35,0.75) circle (0.25);
      }
    \end{tikzonimage}
  \end{column}
  \end{columns}
}
\only<5-7>{
  \begin{columns}[c]
    \begin{column}{0.4\textwidth}
      \begin{itemize}
      \item<5|only@5> $\Lambda_{div}$ does not describe properly evolution
        of upstream profile in JET-VT \parencite{Wynn:2018gp}
      \item<6-7> On TCV \parencite{Vianello:2017ku} $\Lambda_{div}$
        necessary but not sufficient to guarantee increase $\lambda_n$
        in the far SOL
      \item<7|only@7> Additional mechanism suggested among which
        \alert{neutral clogging} 
    \end{itemize}
  \end{column}
  \begin{column}{0.6\textwidth}
    \centering{\includegraphics<5>[width=\textwidth]{../generalFigures/Wynn-HT-VT}}
    \centering{\includegraphics<6-7>[width=\textwidth]{../generalFigures/Vianello-TCV}}
  \end{column}
\end{columns}
}
\centering{\includegraphics<1>[width=1.1\textwidth]{../generalFigures/Various-density-profiles}}
\end{frame}

@@

  \begin{itemize}
    \item \textbf{AUG:} Metallic wall, cryopumps, closed divertor with
      SP on vertical target, short divertor leg
    \item \textbf{TCV:} Carbon wall, completely open divertor,
      operated with relative long divertor leg, no cryopump  
  \end{itemize}
}
\only<2>{
  \vspace{-1.5cm}
  \centering{\includegraphics[width=0.7\textwidth]{../generalFigures/ProbeHead}}
\Fontvi
  \begin{itemize}
    \item \textbf{AUG:} Ion saturation current measured at different
      radial/poloidal position to get velocity from 2D cross-correlation
    \item \textbf{TCV:} Only 1 j$_{sat}$ measurement available,
      different velocity estimate. $v_r$ from
      $\mathbf{E}\times\mathbf{B}$ evaluation from floating potentials
      on CAS, $v_z$ from 2D cross-correlation analysis
  \end{itemize}
}
\only<3>{
  \centering{\includegraphics[width=0.7\textwidth]{../../Experiments/Comparison/pdfbox/ExampleCas}}
  \begin{itemize}
    \item Blob-size is $\delta_b = 0.5 * \tau_b*v_{\perp}$
    \item $\tau_b$ estimated from FWHM of Conditional Avearage
      binormal blob velocity estimated (although differently in the
      two devices)
  \end{itemize}
}
\end{frame}

@@

@@

    \begin{column}{0.6\textwidth}

@@

      \includegraphics<3>[width=.9\textwidth]{../../Experiments/TCV/analysis/pdfbox/CurrentScanConstantBt}

@@

      \includegraphics<7>[width=\textwidth]{../../Experiments/Comparison/pdfbox/UpstreamTargetProfilesConstantBt}

@@

    \begin{column}{0.4\textwidth}

@@

        \item<1|only@1> Shape matched in within the single scan done for each of
          the machine

@@

          There is a factor of 5 difference between
          the two machines due to the very long outer divertor leg of TCV

@@

          avoid earlier disruption. Similar neutral pressure in the

@@

          Greenwald fraction the behaviors at different currents
          almost reconciled for AUG \alert{but not for TCV and at 0.6
            MA for AUG}

@@

          the transition to highly-recycling regime in analogy to
          JET HT \parencite{Wynn:2018gp} \onslide<10>{\alert{but once evolution \textit{vs} greenwald
            fraction is considered the evolution is equivalent between
            different current.}}

@@

\begin{frame}{Current scan at constant q$_{95}$}
  \begin{columns}
    \begin{column}{0.6\textwidth}
      \includegraphics<1>[width=\textwidth]{/Users/vianello/Documents/Fisica/Conferences/IAEA/iaea2018/pdfbox/EquilibriaIpScanConstantQ95}
      \includegraphics<2>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/GeneralIpScanConstantq95}
      \includegraphics<3>[width=.9\textwidth]{../../Experiments/TCV/analysis/pdfbox/CurrentScanConstantQ95}
      \includegraphics<4>[width=\textwidth]{../../Experiments/Comparison/pdfbox/TargetDensityRadiationVsDensityConstantQ95}
      \includegraphics<5>[width=\textwidth]{../../Experiments/Comparison/pdfbox/TargetDensityRadiationVsGreenwaldConstantQ95}
      \includegraphics<6-7>[width=\textwidth]{../../Experiments/Comparison/pdfbox/UpstreamTargetProfilesConstantQ95}
      \includegraphics<8>[width=\textwidth]{../../Experiments/Comparison/pdfbox/AmplitudeTargetVsGreenwaldConstantBt}
      \includegraphics<9>[width=\textwidth]{../../Experiments/Comparison/pdfbox/AmplitudeVsLambdaConstantBt}
      \includegraphics<10>[width=\textwidth]{../../Experiments/Comparison/pdfbox/EfoldBlobConstantQ95}         
      \includegraphics<11>[width=\textwidth]{../../Experiments/Comparison/pdfbox/EfoldLambdaConstantQ95}         
    \end{column}
    \begin{column}{0.4\textwidth}
      \begin{itemize}
        \item<1|only@1> Shape matched in within the single scan even
          though this required for TCV operation with very low
          toroidal field (0.8T)
        \item<1|only@1> The parallel connection length remains almost unchanged
        \item<2|only@2> AUG: As for the case of constant B$_t$ we have
          pretty reproducible behavior matching basically the plasma
          condition in within the current scan
        \item<3|only@3> TCV: Even at such an high density at lower
          current (and lower B$_t$) no sign of target ion flux
          rollover/detachment
        \item<4|only@4> AUG peak target density rollover
          occurs at lower density for lower current as well as
          radiation front movement. For TCV rollover achieved only at
          higher current: \alert{lower I$_p$ does not exhibit sign of
          detachment even if high density is
          achieved. Consistent with lower 
            volumetric recombination from DSS}
         \item<only@5> Interestingly considering the behavior as a
           function of greenwald fraction does not reconcile the
           different current neither on AUG.  
        \only<6-7>{\item For AUG upstream and target profiles still
          exhibit flattening earlier in density at lower current but
          \alert{always at large values of 
          $\Lambda_{div}$}. For TCV no sign of upstream profile flattening \alert{even
          at very large values of $\Lambda_{div}$}
        \item<only@7>  This is due to the fact we did not reach
          divertor detachment which \alert{seems mandatory for
            upstream profile modification}}  
        \item<only@8> AUG: Amplitude evolution as a function of
          greenwald fraction confirms that shoulder starts appearing
          at the onset of highly recycling regime 
        \item<only@9> AUG: Amplitude evolution as a function of $\Lambda_{div}$ 
          still reconcile the explored current scan
        \item<only@10> AUG exhibit consistently an increase of
          $\lambda_n$ with blob-size whereas for TCV the profile
          remains flat consistently with a small variation of
          $\delta_b$
        \item<only@11> And for TCV this is true even at high value of
          $\Lambda_{div}$. \alert{$\Lambda_{div}$ is not sufficient to
          guarantee flat profiles on TCV.}
      \end{itemize}
    \end{column}
  \end{columns}
\end{frame}

\begin{frame}{Neutral behavior investigation on AUG: M. Agostini}
  \only<1>{
    \begin{columns}
      \begin{column}{0.5\textwidth}
        \begin{itemize}
          \item Light emission analysis performed using 2 absolute
            calibrated CCD cameras with D$_{\alpha}$ and D$_{\gamma}$
            filter
          \item Tomographic inversion using pixel technique assuming
            emission only outside the LCFS and neglecting reflection
          \item Inversion technique based on \textbf{S}imultaneous \textbf{A}lgebraic
            \textbf{R}econstruction \textbf{T}echnique (SART) with no
            input from equilibrium and no regolarization
          \item Evolution during density ramp explored
        \end{itemize}
      \end{column}
      \begin{column}{0.5\textwidth}
        \includegraphics[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/Dalpha/Agostini_Fig1.pdf}
      \end{column}
    \end{columns}
  }
  \only<2>{
    \centering{\includgraphics[width=7cm]{../../Experiments/AUG/analysis/pdfbox/Dalpha/Agostini_Fig2.pdf}}
    At the beginning of the fueling ramp emission localized in the HFS
  }
  \only<3>{
    \centering{\includgraphics[width=7cm]{../../Experiments/AUG/analysis/pdfbox/Dalpha/Agostini_Fig3.pdf}}
Radiation starts moving along the separatrix with different patterns between the two radiation
  }
  \only<4>{
    \centering{\includgraphics[width=7cm]{../../Experiments/AUG/analysis/pdfbox/Dalpha/Agostini_Fig4.pdf}}
    Emission propagate also towards the LFS and moves towards the CFR
  }
\end{frame}

\begin{frame}{Heat transport and power balance: D. Carralero}
  \only<1>{
    \begin{columns}
    \begin{column}{0.5\textwidth}
      \begin{itemize}
        \item Using a large database (around 30 discharges) in
          L-Mode detailed ion and electron temperature profiles
          collected
        \item Consistent ion temperature drop observed whenever shoulder
          is observed
      \end{itemize}
    \end{column}
    \begin{column}{0.5\textwidth}
      \includegraphics[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/Carralero_ionTemperature}
    \end{column}
  \end{columns}
}
\only<2>{
  \centering{\includegraphics[width=7cm]{../../Experiments/AUG/analysis/pdfbox/Carralero_powerbalance}}
  \Fontvi
  \begin{itemize}
    \item Parallel heat flux dominated by ion conduction whereas
      perpendicular component dominated by ion convection
    \item In high density regime a substantial fraction of
      P$_{\mathrm{SOL}}$ still remains in the $Q_{\perp}$ for
      $r-r_{\mathrm{LCFS}} \sim 20$ cm
  \end{itemize}
}
\end{frame}
% % %% H-Mode same fueling
\begin{frame}{H-Mode analysis on AUG}
    \Fontvi
  \vspace{-1cm}
  \begin{columns}
  \begin{column}{0.55\textwidth}
    \centering{\includegraphics<1>[height=0.8\textheight]{../../Experiments/AUG/analysis/pdfbox/GeneralComparisonShot34276_34278_34281.pdf}}
    \centering{\includegraphics<2>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/PuffingIpolsola34276_34278_34281}}
  \centering{\includegraphics<3>[height=0.75\textheight]{../../Experiments/AUG/analysis/pdfbox/UpstreamDivertorProfiles34276_34278_34281}}
  \centering{\includegraphics<4>[width=\textwidth]{../../Experiments/Comparison/pdfbox/EfoldSizeShots34276_34278}}
  \centering{\includegraphics<5>[width=\textwidth]{../../Experiments/Comparison/pdfbox/EfoldSizeShots34276_34278_34281}}
  \end{column}
  \begin{column}{0.45\textwidth}
    \begin{itemize}
    \item<1|only@1> We perform a series of shots in H-Mode with 6.5
      total heating power where we changed the fueling and the
      efficiency of cryopumps. Specifically we have
      \begin{itemize}
        \item<1|only@1>\textcolor{colorA}{\# 34276 without the
            cryompumps}
        \item<1|only@1> \textcolor{colorB}{\# 34278 with the same
            fueling as} \textcolor{colorA}{\# 34276} \textcolor{colorB}{but with the cryompump}
        \item<1|only@1> \textcolor{colorC}{\#34281 where we increase
            fueling and seeding trying to mimic the same subdivertor
            pressure as} \textcolor{colorA}{\# 34276}
      \end{itemize}
    \item<1|only@1> Keeping the same fueling with the cryopump clearly
      reduce the pressure in the the sub-divertor area, we don't reach
      clear detachment and the edge density is constant even during
      the fueling ramp. Degraded H-mode reached later without the cryopump

    \item<2|only@2> Different behavior of ELM during the fueling
      ramp. ELM size and frequency changes strongly without the
      cryopump or during extreme fueling case
    \item<3|only@3> The profiles for shot \# 34278 with the cryopum
      and lower fueling remains more steep in all the three timing
      wind and the plasma is still attached. Interestingly for shot \#
      34281 with the cryopumps and higher fueling the detachment is
      more pronounced
    \item<4|only@4> Without the cryopumps, we reached flatter
         profiles with comparable inter-ELM resolved blob-size. This
         indicates strong neutral pressure effects in determining
         upstream profiles
    \item<5|only@5> Increasing the fueling and correspondingly the
      divertor neutral pressure move towards a situation similar to
      \# 34276 without the cryopump
      \end{itemize}
  \end{column}
\end{columns}
\end{frame}

>>>>

\usepackage[style=nature,citestyle=authoryear-comp,defernumbers=true,maxnames=2,firstinits=true,
uniquename=init,backend=bibtex8,arxiv=abs,mcite]{biblatex}
\bibliography{../biblio}
\renewcommand*{\bibfont}{\footnotesize}
\renewcommand*{\citesetup}{\footnotesize}
\usepackage[export]{adjustbox}
\makeatother
\mode<presentation>
\makeatletter
% add a macro that saves its argument
\newcommand{\footlineextra}[1]{\gdef\insertfootlineextra{#1}}
\newbox\footlineextrabox
% for reducing font on a single slide
\newcommand\Fontvi{\fontsize{9}{8.2}\selectfont}
\title{Filamentary transport in high-power H-mode conditions and in no/small-ELM regimes to predict heat and particle loads on PFCs for future devices}
\date{23 May 2018}
\author[N.Vianello]{presented by N. Vianello on behalf of  MST1-Topic 21
  scientific team}
\begin{document}
\tikzstyle{every picture}+=[remember picture]
\maketitle
\begin{frame}{Scientific team}
  \centering{
  Volker Naulin, Matteo Agostini, Diogo Aguiam, Scott Allan, Matthias Bernert, Daniel Carralero Ortiz, 
Stefan Costea, Istvan Cziegler, Hugo De Oliveira, Joaquin Galdon-Quiroga, Gustavo Grenfell, Antti Hakola, 
Codrina Ionita-Schrittwieser, Heinz Isliker, Alexander Karpushov,
Jernej Kovacic, Benoît Labit, Bruce Lipschultz, 
Roberto Maurizio, Ken McClements, Fulvio Militello, Jeppe Miki Busk Olsen, Jens Juul Rasmussen, Timo Ravensbergen, Bernd Sebastian Schneider, Roman Schrittwieser, Jakub Seidl, Monica Spolaore, Christian Theiler, Cedric Kar-Wai Tsui, Kevin Verhaegh, Jose Vicente, 
Nickolas Walkden, Zhang Wei, Elisabeth Wolfrum, W. Vijvers}
\end{frame}

\begin{frame}{Background}
  \only<1>{
\begin{itemize}
\item Role of turbulence transport in the SOL density profile evolution is a well
  know
  feature
  \parencite{LaBombard:2001ks,Rudakov:2005ic,Garcia:2007hh,Carralero:2014gs}. \textcolor{red}{By
    increasing
  density, even without reaching detachment,  SOL density profile tends to flatten}
\end{itemize}}
\only<2-4>{
  \begin{columns}
    \begin{column}{0.5\textwidth}
      \begin{itemize}
      \item AUG and JET (HT) \parencite{Carralero:2015gu} suggest that $\Lambda_{div}=\frac{L_{\parallel}/c_s}{1/\nu_{ei}}\frac{\Omega_i}{\Omega_e}$ dominates this
        process through a transition from
        \textcolor{ta3chameleon}{sheath-limited}
        \onslide<3-4>{to \textcolor{blue}{inertial regime}} 
        \item<4> \textcolor{red}{Tested by changing n$_e$
            and $T_e$ through fueling/seeding/heating}
      \end{itemize}
    \end{column}
    \begin{column}{0.5\textwidth}
      \begin{tikzonimage}[width=\textwidth]{../generalFigures/KoMFig2.png}
        \only<2-4>{
          \draw [thick, ta3chameleon, thick] (0.45,0.25) ellipse (0.23 and 0.1);
      }
        \only<3-4>{
          \draw [thick, blue, thick, rotate=-4] (0.8,0.55) ellipse (0.1 and 0.33);
      }
        \only<4>{
          \draw [thick, red, thick, dashed] (0.35,0.75) circle (0.25);
      }
    \end{tikzonimage}
  \end{column}
  \end{columns}
}
\only<5-7>{
  \begin{columns}[c]
    \begin{column}{0.4\textwidth}
      \begin{itemize}
      \item<5|only@5> $\Lambda_{div}$ does not describe properly evolution
        of upstream profile in JET-VT \parencite{Wynn:2018gp}
      \item<6-7> On TCV \parencite{Vianello:2017ku} $\Lambda_{div}$
        necessary but not sufficient to guarantee increase $\lambda_n$
        in the far SOL
      \item<7|only@7> Additional mechanisms suggested among which
        \alert{effect of divertor neutrals (\emph{clogging mechanism})} 
    \end{itemize}
  \end{column}
  \begin{column}{0.6\textwidth}
    \centering{\includegraphics<5>[width=\textwidth]{../generalFigures/Wynn-HT-VT}}
    \centering{\includegraphics<6-7>[width=\textwidth]{../generalFigures/Vianello-TCV}}
  \end{column}
\end{columns}
}
\centering{\includegraphics<1>[width=1.1\textwidth]{../generalFigures/Various-density-profiles}}
\end{frame}

@@

  \begin{itemize}
    \item \textbf{AUG:} Metallic wall, cryopumps, closed divertor with
      SP on vertical target, short divertor leg
    \item \textbf{TCV:} Carbon wall, completely open divertor,
      operated with relative long divertor leg, no cryopump  
  \end{itemize}
}
\only<2>{
  \vspace{-1.5cm}
  \centering{\includegraphics[width=0.7\textwidth]{../generalFigures/ProbeHead}}
\Fontvi
  \begin{itemize}
    \item \textbf{AUG:} Ion saturation current measured at different
      radial/poloidal position to get velocity from 2D cross-correlation
    \item \textbf{TCV:} A single j$_{sat}$ measurement available,
      which implies different velocity estimate. $v_r$ from
      $\mathbf{E}\times\mathbf{B}$ evaluation from floating potentials
      $v_z$ from 2D cross-correlation analysis ({\small \textit{see
          Tsui,  PoP submitted}})
  \end{itemize}
}
\only<3>{
  \centering{\includegraphics[width=0.7\textwidth]{../../Experiments/Comparison/pdfbox/ExampleCas}}
  \begin{itemize}
    \item Blob-size is $\delta_b = \frac{\tau_b*v_{\perp}}{2}$
    \item $\tau_b$ estimated from FWHM of Conditional Average, 
      binormal blob velocity estimated 
  \end{itemize}
}
\end{frame}

@@

  \Fontvi

@@

    \begin{column}{0.7\textwidth}

@@

      \includegraphics<3>[width=.8\textwidth]{../../Experiments/TCV/analysis/pdfbox/CurrentScanConstantBt}

@@

      \includegraphics<7>[width=.95\textwidth]{../../Experiments/Comparison/pdfbox/UpstreamTargetProfilesConstantBt}

@@

    \begin{column}{0.3\textwidth}

@@

        \item<1|only@1> Shape well matched in both the device

@@

          Factor of 5 difference between
          the two machines

@@

          avoid earlier disruption. Comparable neutral pressure in the

@@

          Greenwald fraction the $n_e^{peak}$ behaviors at different currents
          reconciled for both the machine AUG \alert{partially for
            radiation movement}

@@

          the transition to highly-recycling regime as in 
          JET HT \parencite{Wynn:2018gp} \onslide<10>{\alert{but
              evolution is equivalent if considered \textit{vs} greenwald
            fraction }}

@@

\begin{frame}{Current scan at constant q$_{95}$}
\Fontvi
  \begin{columns}
    \begin{column}{0.7\textwidth}
      \includegraphics<1>[width=\textwidth]{/Users/vianello/Documents/Fisica/Conferences/IAEA/iaea2018/pdfbox/EquilibriaIpScanConstantQ95}
      \includegraphics<2>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/GeneralIpScanConstantq95}
      \includegraphics<3>[width=.8\textwidth]{../../Experiments/TCV/analysis/pdfbox/CurrentScanConstantQ95}
      \includegraphics<4>[width=\textwidth]{../../Experiments/Comparison/pdfbox/TargetDensityRadiationVsDensityConstantQ95}
      \includegraphics<5>[width=\textwidth]{../../Experiments/Comparison/pdfbox/TargetDensityRadiationVsGreenwaldConstantQ95}
      \includegraphics<6-7>[width=.95\textwidth]{../../Experiments/Comparison/pdfbox/UpstreamTargetProfilesConstantQ95}
      \includegraphics<8>[width=\textwidth]{../../Experiments/Comparison/pdfbox/AmplitudeTargetVsGreenwaldConstantBt}
      \includegraphics<9>[width=\textwidth]{../../Experiments/Comparison/pdfbox/AmplitudeVsLambdaConstantBt}
      \includegraphics<10>[width=\textwidth]{../../Experiments/Comparison/pdfbox/EfoldBlobConstantQ95}         
      \includegraphics<11>[width=\textwidth]{../../Experiments/Comparison/pdfbox/EfoldLambdaConstantQ95}         
    \end{column}
    \begin{column}{0.3\textwidth}
      \begin{itemize}
        \item<1|only@1> Shape matched in within the single scan even
          though this required for TCV operation with very low
          toroidal field (0.8T)
        \item<1|only@1> The parallel connection length remains almost unchanged
        \item<2|only@2> AUG: As for the case of constant B$_t$ we have
          pretty reproducible behavior matching basically the plasma
          condition in within the current scan
        \item<3|only@3> TCV: Even at such an high density at lower
          current (and lower B$_t$) no sign of target ion flux
          rollover/detachment
        \item<4|only@4> AUG peak target density rollover
          occurs at lower density for lower current as well as
          radiation front movement. For TCV rollover achieved only at
          higher current: \alert{lower I$_p$ does not exhibit sign of
          detachment even if high density is
          achieved. Consistent with lower 
            volumetric recombination from DSS}
         \item<only@5> Interestingly considering the behavior as a
           function of greenwald fraction does not reconcile the
           different current neither on AUG.  
        \only<6-7>{\item For AUG upstream and target profiles still
          exhibit flattening earlier in density at lower current but
          \alert{always at large values of 
          $\Lambda_{div}$}. For TCV no sign of upstream profile flattening \alert{even
          at very large values of $\Lambda_{div}$}
        \item<only@7>  This is due to the fact we did not reach
          divertor detachment which \alert{seems mandatory for
            upstream profile modification}}  
        \item<only@8> AUG: Amplitude evolution as a function of
          greenwald fraction confirms that shoulder starts appearing
          at the onset of highly recycling regime 
        \item<only@9> AUG: Amplitude evolution as a function of $\Lambda_{div}$ 
          still reconcile the explored current scan
        \item<only@10> AUG exhibit consistently an increase of
          $\lambda_n$ with blob-size whereas for TCV the profile
          remains flat consistently with a small variation of
          $\delta_b$
        \item<only@11> And for TCV this is true even at high value of
          $\Lambda_{div}$. \alert{$\Lambda_{div}$ is not sufficient to
          guarantee flat profiles on TCV.}
      \end{itemize}
    \end{column}
  \end{columns}
\end{frame}

\begin{frame}{Neutral behavior investigation on AUG}
  \only<1>{
    \begin{columns}
      \begin{column}{0.5\textwidth}
        \begin{itemize}
          \item Light emission analysis performed using 2 absolute
            calibrated CCD cameras with D$_{\alpha}$ and D$_{\gamma}$
            filter
          \item Tomographic inversion using pixel technique assuming
            emission only outside the LCFS and neglecting reflection
          \item Inversion technique based on \textbf{S}imultaneous \textbf{A}lgebraic
            \textbf{R}econstruction \textbf{T}echnique (SART) with no
            input from equilibrium and no regolarization
          \item Evolution during density ramp explored
        \end{itemize}
      \end{column}
      \begin{column}{0.5\textwidth}
        \includegraphics[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/Dalpha/Agostini_Fig1.pdf}
      \end{column}
    \end{columns}
  }
  \only<2>{
    \centering{\includegraphics[width=10cm]{../../Experiments/AUG/analysis/pdfbox/Dalpha/Agostini_Fig2.pdf}}

    \vspace{1cm}

    At the beginning of the fueling ramp emission localized in the HFS
  }
  \only<3>{
    \centering{\includegraphics[width=10cm]{../../Experiments/AUG/analysis/pdfbox/Dalpha/Agostini_Fig3.pdf}}

    \vspace{1cm}

Radiation starts moving along the separatrix with different patterns between the two radiation
  }
  \only<4>{
    \centering{\includegraphics[width=10cm]{../../Experiments/AUG/analysis/pdfbox/Dalpha/Agostini_Fig4.pdf}}

    \vspace{1cm}

    Emission propagate also towards the LFS and moves towards the CFR
  }

  \vspace{1cm}

{\begin{flushleft}
{\small \textit{(M. Agostini)}}
  \end{flushleft}
}
\end{frame}

\begin{frame}{Heat transport and power balance}
  \only<1>{
    \begin{columns}
    \begin{column}{0.5\textwidth}
      \begin{itemize}
        \item Using a large database (around 30 discharges) in
          L-Mode detailed ion and electron temperature profiles
          collected
        \item Consistent ion temperature drop observed whenever shoulder
          is observed
      \end{itemize}
    \end{column}
    \begin{column}{0.5\textwidth}
      \includegraphics[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/Carralero_ionTemperature}
    \end{column}
  \end{columns}
}
\only<2>{
  \centering{\includegraphics[width=10cm]{../../Experiments/AUG/analysis/pdfbox/Carralero_powerbalance}}
  \begin{itemize}
    \item Parallel heat flux dominated by ion conduction whereas
      perpendicular component dominated by ion convection
    \item In high density regime a substantial fraction of
      P$_{\mathrm{SOL}}$ still remains in the $Q_{\perp}$ for
      $r-r_{\mathrm{LCFS}} \sim 20$ cm
  \end{itemize}
}

{\begin{flushleft}
{\small \textit{(D. Carralero)}}
  \end{flushleft}
}
\end{frame}
% % %% H-Mode same fueling
\begin{frame}{H-Mode analysis on AUG}
    \Fontvi
  \vspace{-1cm}
  \begin{columns}
  \begin{column}{0.55\textwidth}
    \centering{\includegraphics<1>[height=0.8\textheight]{../../Experiments/AUG/analysis/pdfbox/GeneralComparisonShot34276_34278_34281.pdf}}
    \centering{\includegraphics<2>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/PuffingIpolsola34276_34278_34281}}
  \centering{\includegraphics<3>[height=0.75\textheight]{../../Experiments/AUG/analysis/pdfbox/UpstreamDivertorProfiles34276_34278_34281}}
  \centering{\includegraphics<4>[width=\textwidth]{../../Experiments/Comparison/pdfbox/EfoldSizeShots34276_34278}}
  \centering{\includegraphics<5>[width=\textwidth]{../../Experiments/Comparison/pdfbox/EfoldSizeShots34276_34278_34281}}
  \end{column}
  \begin{column}{0.45\textwidth}
    \begin{itemize}
    \item<1|only@1> We perform a series of shots in H-Mode with 6.5
      total heating power where we changed the fueling and the
      efficiency of cryopumps. Specifically we have
      \begin{itemize}
        \item<1|only@1>\textcolor{colorA}{\# 34276 without the
            cryompumps}
        \item<1|only@1> \textcolor{colorB}{\# 34278 with the same
            fueling as} \textcolor{colorA}{\# 34276} \textcolor{colorB}{but with the cryompump}
        \item<1|only@1> \textcolor{colorC}{\#34281 where we increase
            fueling and seeding trying to mimic the same subdivertor
            pressure as} \textcolor{colorA}{\# 34276}
      \end{itemize}
    \item<1|only@1> Keeping the same fueling with the cryopump clearly
      reduce the pressure in the the sub-divertor area, we don't reach
      clear detachment and the edge density is constant even during
      the fueling ramp. Degraded H-mode reached later without the cryopump

    \item<2|only@2> Different behavior of ELM during the fueling
      ramp. ELM size and frequency changes strongly without the
      cryopump or during extreme fueling case
    \item<3|only@3> The profiles for shot \# 34278 with the cryopump
      and lower fueling remains more steep in all the three time
      windows and the plasma is still attached. Interestingly for shot \#
      34281 with the cryopumps and higher fueling the detachment is
      more pronounced
    \item<4|only@4> The shoulder is almost comparable 
      w.r.t. L-Mode plasma (even if higher density is needed)
    \item<5|only@5> Without the cryopumps, we reached flatter
         profiles with comparable inter-ELM resolved blob-size. This
         indicates strong neutral pressure effects in determining
         upstream profiles
    \item<6|only@6> Increasing the fueling and correspondingly the
      divertor neutral pressure move towards a situation similar to
      \# 34276 without the cryopump
      \end{itemize}
  \end{column}
\end{columns}
\end{frame}
